### 2018-07-02 paper/7-related.tex
Work on S7
More tweaks to S7

\begin{itemize}
\item \Ninja~\cite{ninja} combines the dependency strategy of \Make with the
validating traces of \Shake~--~our associated implementation provides such a
combination. Ninja is also capable of modelling rules that produce multiple
results, a limited form of polymorphism \S\ref{sec-polymorphism}.

@@

\item \Buck~\cite{buck} is very similar to \Bazel at the level of abstraction presented here.

\item \CloudBuild~\cite{esfahani2016cloudbuild}
differs from \Bazel by allowing non-determinism~\S\ref{sec-non-determinism}, thus more closely modelling
our original definition of \Bazel from \S\ref{sec-implementation-cloud}.

\item \Nix~\cite{dolstra2004nix} has coarse-grained dependencies, with precise
hashing of dependencies and downloading of precomputed build products. When
combined with \cmd{import-from-derivation}, \Nix can also be considered monadic,
making it similar to \Cloud \Shake
from~\S\ref{sec-implementation-cloud}.
However, \Nix is not intended as a build system, and the coarse grained nature
(packages, not individual files) makes it targeted to a different purpose.
% John Ericson suggested in a blog comment that nix may be somewhat monadic, see:
% \url{https://blogs.ncl.ac.uk/andreymokhov/cloud-and-dynamic-builds/\#comment-1849}.

>>>>

\begin{itemize}
\item \Ninja~\cite{ninja} combines the dependency strategy of \Make with the
validating traces of \Shake~--~our associated implementation provides such a
combination. \Ninja~is also capable of modelling rules that produce multiple
results, a limited form of polymorphism \S\ref{sec-polymorphism}.

@@

\item \CloudBuild~\cite{esfahani2016cloudbuild} uses constructive traces with a topological sort.

\item \Buck~\cite{buck} uses deep constructive traces with a topological sort,
meaning that it disallows non-determinism~\S\ref{sec-non-determinism}.

\item \Nix~\cite{dolstra2004nix} has coarse-grained dependencies, with precise
hashing of dependencies and downloading of precomputed build products. When
combined with \cmd{import-from-derivation}, \Nix provides monadic dependencies.
\Nix is not primarily intended as a build system, and the coarse grained nature
(packages, not individual files) makes it targeted to a different purpose.
% John Ericson suggested in a blog comment that nix may be somewhat monadic, see:
% \url{https://blogs.ncl.ac.uk/andreymokhov/cloud-and-dynamic-builds/\#comment-1849}.
